Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-19 Ch1_movement_rates/Ch1_Figures.Rmd
Getting somewhere!!

points_plot <- function(seed.data, summ.data, s.size = 1000, xylims=1250, lalpha = 0.5, scenario = NULL){

  seed.data %>% 
    drop_na(s.id) %>% 
    mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>% 
    #slice_head(., n = s.size) %>% 
    sample_n(s.size) %>% 
      ggplot(., aes(x = xloc, y = yloc, color = dispcat)) +
      geom_point(alpha = lalpha) +
      labs(subtitle = scenario) +
      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw() +
      theme(legend.position = "none",
            axis.title = element_blank()) +
       NULL -> seedlocplot

  # summ.data %>%
  #   #cp.summ.df %>%
  #   sample_n(s.size) %>%
  #   #slice_head(., n = s.size/5) %>%
  #   #pivot_longer(., cols = c(dsprsn, av.disp)) %>%
  #   #ggplot(., aes(x = name, y = value)) +
  #   ggplot(., aes(y = dsprsn)) +
  #   #geom_violin() +
  #   #geom_jitter(position = position_jitter(0.1), alpha = lalpha) +
  #   geom_boxplot(width = 0.1) +
  #   #geom_point(aes(x=0, color = run)) +
  #   lims(y = c(0, 650)) +
  #   labs(y = "Dispersion in meters") +
  #   theme_bw() +
  #   NULL -> dispersionplot
  # 
  # summ.data %>%
  #   #cp.summ.df %>%
  #   sample_n(s.size) %>%
  #   #slice_head(., n = s.size/5) %>%
  #   #pivot_longer(., cols = c(dsprsn, av.disp)) %>%
  #   #ggplot(., aes(x = name, y = value)) +
  #   ggplot(., aes(y = av.disp)) +
  #   #geom_violin() +
  #   #geom_jitter(position = position_jitter(0.1), alpha = lalpha) +
  #   geom_boxplot(width = 0.1) +
  #   #geom_point(aes(x=0, color = run)) +
  #   lims(y = c(0, 1300)) +
  #   labs(y = "Dispersal in meters") +
  #   theme_bw() +
  #   NULL -> dispersalplot
  # 
  # plot_grid(seedlocplot, dispersalplot, dispersionplot, ncol=3, rel_widths = c(2,1,1))
  # 
}

A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df, scenario = "CP")

#A

B <- points_plot(seed.data = pp.df, summ.data = pp.summ.df, scenario = "PP")
C <- points_plot(seed.data = np.df, summ.data = np.summ.df, scenario = "NP")

seedplots2d <- plot_grid(A, B, C, ncol = 3)

# To do:
# Remove xy labels
# change colors so only over 500 shows blue
# remove legends
# Add boxplots for dispersion next to it
# Am I adding dispersal?
# For final figure increase sample size to 50,000 so we have 10% of the data visualized.

@@

disp_df %>%
  group_by(., model) %>%
  sample_n(., 50000) %>%
  #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  #scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Dispersion in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_blank()) -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 50000) %>%
  mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = av.disp, x = model, color = dispcat)) +
  geom_boxplot() +
  geom_point(color = "grey", alpha = 0.5) +
  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Average dispersal in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_blank()) -> p_dispersal

plot_grid(p_dispersal, p_dispersion)

>>>>

points_plot <- function(seed.data, summ.data, s.size = 5000, xylims=1250, lalpha = 0.5, scenario = NULL, twoplots = FALSE){

  seed.data %>% 
    drop_na(s.id) %>% 
    mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>% 
    #slice_head(., n = s.size) %>% 
    sample_n(s.size) %>% 
      ggplot(., aes(x = xloc, y = yloc, color = dispcat)) +
      geom_point(alpha = lalpha) +
      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
      geom_text(label = scenario, x = -1000, y = -1000, color = "black") +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw() +
      theme(legend.position = "none",
            axis.title = element_blank()) +
       NULL -> seedlocplot

    if(twoplots == TRUE){

          summ.data %>% 
    #drop_na(s.id) %>% 
    mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>% 
    #slice_head(., n = s.size) %>% 
    sample_n(s.size*5) %>% 
      ggplot(., aes(x = x, y = y, color = dispcat)) +
      geom_point(alpha = lalpha) +
      labs(subtitle = scenario) +
      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw() +
      theme(legend.position = "none",
            axis.title = element_blank()) +
       NULL -> summaryplot

      plot_grid(seedlocplot, summaryplot, ncol = 2)
    }

  else{seedlocplot}
}

# A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df, scenario = "CP", twoplots = TRUE)
# A

A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df, scenario = "CP")
B <- points_plot(seed.data = pp.df, summ.data = pp.summ.df, scenario = "PP")
C <- points_plot(seed.data = np.df, summ.data = np.summ.df, scenario = "NP")

seedplots2d <- plot_grid(A, B, C, ncol = 3, labels = "A")
#seedplots2d

@@

disp_df %>%
  group_by(., model) %>%
  sample_n(., 5000) %>%
  #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  #scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Dispersion in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 5000) %>%
  #mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = av.disp, x = model
                #, color = dispcat
                )) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Average dispersal in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) -> p_dispersal

disp2_plot <- plot_grid(p_dispersal, p_dispersion, ncol = 2, labels = c("B", "C"))
#disp2_plot

```{r fig.height=9}
plot_grid(seedplots2d, disp2_plot, nrow = 2)
